---
title: "9041 Assignment 2"
author: Wanying Lu
date: Sep.26 2026
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---
```{r}
library(tidyverse)
library(psych)
library(readxl)
library(gt)
library(janitor)

anxiety.df <- read_excel("./Attachment_Anxiety_Data.xlsx")

anxiety.clean.df <- anxiety.df |>
mutate(gender_char = case_when(Gender == 1 ~ "Male",
                               Gender == 2 ~ "Female"),
       ethnicity_char = case_when(Ethnicity == 1 ~ "White/Caucasian",
                                  Ethnicity == 2 ~ "Asian/Asian British",
                                  Ethnicity == 5 ~ "Other ethnic group",
                                  Ethnicity == 6 ~ "Prefer not to say"),
       across(SA_1:SEst_10, as.integer))

SA_keys<- list (avg_SA=c("SA_1","SA_2","SA_3","SA_4","-SA_5","SA_6","SA_7","SA_8",
                       "-SA_9","SA_10","-SA_11","SA_12","SA_13","SA_14","SA_15","SA_16",
                       "SA_17","SA_18","SA_19","SA_20"))
AA_keys<- list (avg_AA=c("AA_1","AA_2","AA_3","AA_4","AA_5","AA_6","AA_7","AA_8",
                       "AA_9"))
SEst_keys<- list (avg_SEst=c("SEst_1","-SEst_2","SEst_3","SEst_4","-SEst_5","-SEst_6",
                       "SEst_7","-SEst_8","-SEst_9","SEst_10"))

SA_scores<-scoreItems(SA_keys, anxiety.clean.df, totals=F, min=0, max=4)
AA_scores<-scoreItems(AA_keys, anxiety.clean.df, totals=F, min=1, max=7)
SEst_scores<-scoreItems(SEst_keys, anxiety.clean.df, totals=F, min=1, max=4)

SA_scores.df   <- as.data.frame(SA_scores$scores)
AA_scores.df   <- as.data.frame(AA_scores$scores)
SEst_scores.df <- as.data.frame(SEst_scores$scores)

allscores.df <- cbind(SA_scores.df,AA_scores.df,SEst_scores.df)

anxiety.scored.df <- cbind(anxiety.clean.df, allscores.df)

anxiety.final.df<- anxiety.scored.df|>
  select(URN, gender_char,ethnicity_char,avg_SA,avg_AA,avg_SEst)

summary <- anxiety.final.df |>
  select(avg_SA, avg_AA, avg_SEst) |>
  describe()|>
  mutate(across(where(is.numeric), ~ round(.x, 2)))

summary$Scales <- c(
  "Social Interaction Anxiety",
  "Attachment-Related Anxiety",
  "Self-Esteem")
```

## Intro
This assignment analyzes the Attachment and Social Anxiety dataset by Jacob Lincoln, Liesbeth Tip, and Sofia De La Fuente Garcia, focusing on attachment-related anxiety, social interaction anxiety, and self-esteem.

## Methods
Participants were recruited via the University of Edinburgh’s online learning portal and social media platforms, as well as through word-of-mouth. A flyer with a link to the study was shared on these platforms along with a standard message explaining the purpose of the study, the inclusion criteria (i.e., must be over the age of 18), and the contact details of one of the researchers. 

The participants followed a link to the questionnaire, which was created using the Online Surveys platform. Participants responded to 3 questionnaires to measure 1) Attachment-related anxiety, 2) Social anxiety and 3) Self-esteem. They were also asked to report their gender, age group, relationship status and ethnicity. 

### Participants
```{r}
sample_size <- nrow(anxiety.final.df)
```

There were `r sample_size` participants in the study. Table 1 presents the demographic information of the participants.

```{r}
demographic.table <- anxiety.final.df |>
  tabyl(gender_char, ethnicity_char)|>
  select(
    gender_char,
    'White/Caucasian',
    'Asian/Asian British',
    'Other ethnic group',
    'Prefer not to say'
  )

demographic.gt <- demographic.table |>
  gt() |>
  tab_header(
    title = "Table 1 Participant Demographics"
  )|>
  cols_label(
    gender_char="Gender"
  )

demographic.gt
```

### Measures
There are three scales used in this analysis:

1. Experiences in Close Relationships Scale (shortened Attachment-Related Anxiety subscale). This subscale was shortened by only including the nine items that loaded most strongly on the Anxiety subscale in a factor analysis conducted by Sibley, Fischer & Liu (2005). This scale had a Cronbach's alpha of `r round(AA_scores$alpha, 2)`.
2. Social Interaction Anxiety Scale, with a Cronbach's alpha of `r round(SA_scores$alpha, 2)`.
3. Rosenberg Self-Esteem Scale, which had a Cronbach's alpha of `r round(SEst_scores$alpha, 2)`.


## Data Analysis Strategy
Items were reverse-keyed in the scoring keys before calculating the scale scores. Items 5, 9, and 11 were reverse-keyed for Social Interaction Anxiety, while Items 2, 5, 6, 8, and 9 were reverse-keyed for Self-Esteem. No items were reverse-keyed for Attachment-Related Anxiety. Reverse-keyed items were indicated with a minus sign (-) in the scoring keys and were handled by scoreItems().

## Results

```{r}

alphas <- round(c(AA_scores$alpha, SA_scores$alpha,SEst_scores$alpha),2)

summary.table <- summary |>
  select(Scales, mean, median, sd, range)

summary.table <- cbind(summary.table, alpha = alphas)

score.table <- summary.table |>
  gt() |>
  tab_header(
    title = "Table 2 Summary Statistics for Attachment and Social Anxiety"
  ) |>
  cols_label(
    Scales = "Scale",
    mean = "Mean",
    median = "Median",
    sd = "SD",
    range = "Range",
    alpha = "Cronbach's Alpha"
  )

```

Table 2 summarizes the descriptive statistics and internal consistency of the three scales used in the study: Attachment-Related Anxiety, Social Interaction Anxiety, and Self-Esteem. The table presents the mean, median, standard deviation, range, and Cronbach’s alpha for each scale. The mean score for Attachment-Related Anxiety was `r round(summary.table$mean[summary.table$Scales == "Attachment-Related Anxiety"], 2)`. The mean score for Social Interaction Anxiety was `r round(summary.table$mean[summary.table$Scales == "Social Interaction Anxiety"], 2)`, and the mean score for Self-Esteem was `r round(summary.table$mean[summary.table$Scales == "Self-Esteem"], 2)`.

```{r}
score.table
```

```{r}

anxiety.female.df <- anxiety.scored.df |>
  filter(gender_char == "Female")

female_sample_size <- nrow(anxiety.female.df)

female.summary <- anxiety.female.df |>
  select(avg_AA, avg_SA, avg_SEst) |>
  describe()|>
  mutate(across(where(is.numeric), ~ round(.x, 2)))

female.summary$Scales <- c(
  "Attachment-Related Anxiety",
  "Social Interaction Anxiety",
  "Self-Esteem")

female.summary.table <- female.summary |>
  select(Scales, mean, median, sd, range)

female.AA_scores <- scoreItems(AA_keys, anxiety.female.df,totals = F, min = 1, max = 7)
female.SA_scores <- scoreItems(SA_keys, anxiety.female.df,totals = F, min = 0, max = 4)
female.SEst_scores <- scoreItems(SEst_keys, anxiety.female.df,totals = F, min = 1, max = 4)

female.alphas <- round(c(
  female.AA_scores$alpha,
  female.SA_scores$alpha,
  female.SEst_scores$alpha), 2)

female.summary.table <- cbind(
  female.summary.table,
  alpha = female.alphas)

female.score.table <- female.summary.table |>
  gt() |>
  tab_header(
    title = "Table 3 Summary Statistics for Female Participants"
  ) |>
  cols_label(
    Scales = "Scale",
    mean = "Mean",
    median = "Median",
    sd = "SD",
    range = "Range",
    alpha = "Cronbach's Alpha"
  )
```

Table 3 presents the descriptive statistics and internal consistency of the three scales for female participants only. The mean score for Attachment-Related Anxiety was `r round(female.summary.table$mean[female.summary.table$Scales == "Attachment-Related Anxiety"], 2)`, the mean score for Social Interaction Anxiety was `r round(female.summary.table$mean[female.summary.table$Scales == "Social Interaction Anxiety"], 2)`, and the mean score for Self-Esteem was `r round(female.summary.table$mean[female.summary.table$Scales == "Self-Esteem"], 2)`. Cronbach's alpha values ranged from .86 to .94 across the three scales.
```{r}
female.score.table
```
